
% Document settings
\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[pdftex]{graphicx}
\usepackage{multirow}
\usepackage{setspace}
\pagestyle{plain}
\setlength\parindent{0pt}

\begin{document}

% Course information
\begin{tabular}{ l l }
  \multirow{3}{*} & \LARGE Course Code: 1637583 \\\\
      & \LARGE Introduction to East Asian Pop Culture \\\\
  & \LARGE MWF, 10-12 AM, MLK \\\\
\end{tabular}
\vspace{10mm}

% Professor information
\begin{tabular}{ l l }
  \multirow{6}{*} & \large Sisi Wu\\\\
  & \large sisiwu@gmail.com \\
  & \large easyasianpopculture.com \\
  & \large Dwinelle 498  \\
  & \large Office Hours: TBD \\
  & \large (163) 837-5409 \\
\end{tabular}
\vspace{5mm}
\begin{center}  \\
\end{center}

% Course details
\textbf {\large \\ Course Description:} The purpose of this course is to exchange and enhance our understanding of East Asian pop culture in an innovative and interdisciplinary framework. In recent years, there has been an explosion of global interest in the pop culture of East Asia. Although it has proved incredibly fascinating, it remains an underdeveloped area in interdisciplinary research. This course seeks to undertake an inventory of diverse discourses on East Asian pop culture in terms of identity, interest, and power. \\
\textbf {Prerequisite(s):} None.

\textbf {Note(s):} A minimum grade of C is required in this course to progress to COURSE. 

\textbf {Credit Hours:} 3 \\

\textbf {\large Text(s):} \emph{Conceptualizing an East Asian popular culture}

\textbf {Author(s):} Chua Beng Huat\\

\textbf {\large Course Objectives:} \\
At the completion of this course, students will be able to:
\begin{enumerate} \itemsep-0.4em
  \item We will discuss the identity-dimension of pop culture such as the formation of a transnational identity, as well as the clash of national identity in the context of pop culture in East Asia.
  \item We will explore the power-dimension of East Asian pop culture in terms of Joseph Nye’s notion of soft power which denotes the ability to shape the preferences of others and create a positive influence by means of attraction.
  \item We will examine the interest- dimension of East Asian pop culture including the spin-off effects of the Korean Wave and Nation Branding.

\end{enumerate}

% I recommend using \newpage here if necessary
\textbf {\large Grade Distribution:} \\
\hspace*{40mm}
\begin{tabular}{ l l }

Assignments & 25\% \\
Project & 25\% \\
Quizzes  & 10\% \\
Midterm Exam  & 20\% \\
Final Exam  & 20\%
\end{tabular} \\\\

\textbf {\large Letter Grade Distribution:} \\\\
\hspace*{40mm}
\begin{tabular}{ l l | l l }
\textgreater= 93.00 & A & 73.00 - 76.99 & C \\
90.00 - 92.99 & A-  & 70.00 - 72.99 & C- \\
87.00 - 89.99 & B+  & 67.00 - 69.99 & D+ \\
83.00 - 86.99 & B  & 63.00 - 66.99 & D \\
80.00 - 82.99 & B-  & 60.00 - 62.99 & D- \\
77.00 - 79.99 & C+  & \textless= 59.99 & F \\
\end{tabular} \\

% Course Policies.
\textbf {\large Course Policies:}
\begin{itemize}
\item \textbf {General}
\begin{itemize}
\item Computers are not to be used unless instructed to do so.
\item Quizzes and exams are closed book, closed notes.
\item \textbf {No makeup quizzes or exams will be given.}
\end{itemize}
\item \textbf {Grades}
\begin{itemize}
\item Grades in the \textbf{C} range represent performance that \textbf{meets expectations}; Grades in the \textbf{B} range represent performance that is \textbf{substantially better} than the expectations; Grades in the \textbf{A} range represent work that is \textbf{excellent}.
\item Grades will be maintained in the LMS course shell. Students are responsible for tracking their progress by referring to the online gradebook.
\end{itemize}
\item \textbf {Labs and Assignments}
\begin{itemize}
\item Students are expected to work independently. \textbf{Offering} and \textbf{accepting} solutions from others is an act of \textbf{plagiarism}, which is a serious offense and \textbf{all involved parties will be penalized according to the Academic Honesty Policy}. Discussion amongst students is encouraged, but when in doubt, direct your questions to the professor, tutor, or lab assistant.
\item \textbf{No late assignments will be accepted under any circumstances}.
\end{itemize}
\item \textbf{Attendance and Absences}
\begin{itemize}
\item Attendance is expected and will be taken each class. You are allowed to miss \textbf{1} class during the semester without penalty. Any further absences will result in point and/or grade deductions. 
\item Students are responsible for all missed work, regardless of the reason for absence. It is also the absentee's responsibility to get all missing notes or materials. 
\end{itemize}
\end{itemize}

% College Policies
\textbf {\largeAcademic Honesty Policy Summary:} 

\textbf{Introduction}

\hspace{3mm}
\hangindent=5mm In addition to skills and knowledge, COLLEGE/UNIVERSITY aims to teach students appropriate Ethical and Professional Standards of Conduct. The Academic Honesty Policy exists to inform students and Faculty of their obligations in upholding the highest standards of professional and ethical integrity. All student work is subject to the Academic Honesty Policy. Professional and Academic practice provides guidance about how to properly cite, reference, and attribute the intellectual property of others. Any attempt to deceive a faculty member or to help another student to do so will be considered a violation of this standard.


\textbf{Instructor's Intended Purpose}

\hspace{3mm}
\hangindent=5mm The student's work must match the instructor's intended purpose for an assignment. While the instructor will establish the intent of an assignment, each student must clarify outstanding questions of that intent for a given assignment. 


\textbf{Unauthorized/Excessive Assistance}

\hspace{3mm}
\hangindent=5mm The student may not give or get any unauthorized or excessive assistance in the preparation of any work.

\textbf{Authorship}

\hspace{3mm}
\hangindent=5mm The student must clearly establish authorship of a work. Referenced work must be clearly documented, cited, and attributed, regardless of media or distribution. Even in the case of work licensed as public domain or Copyleft, (See: http://creativecommons.org/) the student must provide attribution of that work in order to uphold the standards of intent and authorship.


\textbf{Declaration}

\hspace{3mm}
\hangindent=5mm Online submission of, or placing one's name on an exam, assignment, or any course document is a statement of academic honor that the student has not received or given inappropriate assistance in completing it and that the student has complied with the Academic Honesty Policy in that work.


\textbf{Consequences}

\hspace{3mm}
\hangindent=5mm  \An instructor may impose a sanction on the student that varies depending upon the instructor's evaluation of the nature and gravity of the offense.  Possible sanctions include but are not limited to, the following: (1) Require the student to redo the assignment; (2) Require the student to complete another assignment; (3) Assign a grade of zero to the assignment; (4) Assign a final grade of ``F'' for the course. A student may appeal these decisions according to the Academic Grievance Procedure. (See the relevant section in the Student Handbook.) Multiple violations of this policy will result in a referral to the Conduct Review Board for possible additional sanctions. \\

The full text of the Academic Honesty Policy is in the \emph{Student Handbook}.

% data research disclosure 
\textbf {\large Data for Research Disclosure}:

Any and all results of in-class and out-of-class assignments and examinations are data sources for research and may be used in published research. All such use will always be anonymous.

\newpage

% Course Outline
\textbf {\large Tentative Course Outline}:

The weekly coverage might change as it depends on the progress of the class.  However, you must keep up with the reading assignments.

\begin{table}[h!]
\normalsize % The size of the table text can be changed depending on content. Remove if desired.
\begin{tabular}{ | c | c | }
\hline
\textbf{Week} & \textbf{Content} \\
\hline
Week 1 & \begin{minipage}{.85\textwidth}
\begin{itemize} \itemsep-0.4em
	\vspace{1mm}
	\item Welcome to the Course
	\item Pre-assignment: come to the lecture prepare to talk about what you most associate with east asian pop culture; it could be a person, a film, a TV show, a song - anything
	\vspace{1mm}
\end{itemize}
\end{minipage} \\
\hline
Week 2 & \begin{minipage}{.85\textwidth}
\begin{itemize} \itemsep-0.4em
	\vspace{1mm}
	\item China: from Ming-Qing Huaben to modern fanfics
	\item Reading assignment: TV Show "The Story of the Stone" 1987 version; Book "The Story of the Stone"; TV Show "Empresses in the Palace"; also reading fanfics on lofter and jinjiang is not required but highly recommended 
	\vspace{1mm}
\end{itemize}
\end{minipage} \\
\hline
Week 3 & \begin{minipage}{.85\textwidth}
\begin{itemize} \itemsep-0.4em
	\vspace{1mm}
	\item Japan: Japanese Movie = Anime + Tragedies?
	\item Reading assignment: any three movies from works of Koreeda Hirokazu, Shunji Iwai, Miyazaki Hayao and Shinkai Makoto
	\vspace{1mm}
\end{itemize}
\end{minipage} \\
\hline
Week 4 & \begin{minipage}{.85\textwidth}
\begin{itemize} \itemsep-0.4em
	\vspace{1mm}
	\item Korea: why K-POP and K-Drama so popular around the world?
	\item Pre-assignment: conduct and independent project and compile results to a report
	\vspace{1mm}
\end{itemize}
\end{minipage} \\
\hline
Week 5 & \begin{minipage}{.85\textwidth}
\begin{itemize} \itemsep-0.4em
	\vspace{1mm}
	\item Student Presentations
	\item Present your independent project
	\vspace{1mm}
\end{itemize}
\end{minipage} \\
\hline
Week 6 & \begin{minipage}{.85\textwidth}
\begin{itemize} \itemsep-0.4em
	\vspace{1mm}
	\item Guest Speaker Lecture
	\item Reading assignment: to be decided
	\vspace{1mm}
\end{itemize}
\end{minipage} \\
\hline
Week 7 & \begin{minipage}{.85\textwidth}
\begin{itemize} \itemsep-0.4em
	\vspace{1mm}
	\item Taiwan New Waves and its influence in East Asia
	\item Reading assignment: A One and a Two by Edward Yang; A Brighter Summer Day by Edward Yang; Any two movies by Shunji Iwai
	\vspace{1mm}
\end{itemize}
\end{minipage} \\
\hline
Week 8 & \begin{minipage}{.85\textwidth}
\begin{itemize} \itemsep-0.4em
	\vspace{1mm}
	\item BAMFA Movie Day
	\item Movie to be decided
	\vspace{1mm}
\end{itemize}
\end{minipage} \\
\hline
Week 9 & \begin{minipage}{.85\textwidth}
\begin{itemize} \itemsep-0.4em
	\vspace{1mm}
	\item Idols and Fan Economy
	\item No prior reading required
	\vspace{1mm}
\end{itemize}
\end{minipage} \\
\hline
Week 10 & \begin{minipage}{.85\textwidth}
\begin{itemize} \itemsep-0.4em
	\vspace{1mm}
	\item Guest Speaker Lecture
	\item Reading assignment: to be decided
	\vspace{1mm}
\end{itemize}
\end{minipage} \\
\hline
Week 11 & \begin{minipage}{.85\textwidth}
\begin{itemize} \itemsep-0.4em
	\vspace{1mm}
	\item Student proposed lecture topic
	\item Reading assignment: to be decided
	\vspace{1mm}
\end{itemize}
\end{minipage} \\
\hline
Week 12 & \begin{minipage}{.85\textwidth}
\begin{itemize} \itemsep-0.4em
	\vspace{1mm}
	\item Student proposed lecture topic
	\item Reading assignment: to be decided
	\vspace{1mm}
\end{itemize}
\end{minipage} \\
\hline
Week 13 & \begin{minipage}{.85\textwidth}
\begin{itemize} \itemsep-0.4em
	\vspace{1mm}
	\item Semester Recap
	\item None
	\vspace{1mm}
\end{itemize}
\end{minipage} \\
\hline
Week 14 & \begin{minipage}{.85\textwidth}
\begin{itemize} \itemsep-0.4em
	\vspace{1mm}
	\item End of semester party
	\item None
	\vspace{1mm}
\end{itemize}
\end{minipage} \\
\hline
\end{tabular} 
\end{table}

\end{document}



